### 2019-02-13 sections/comparison.tex
add some more todos

Concurrency is the source of parallelism: two things are done at the same time.
%
Using tasks $t_1$ and $t_2$, the parallel combination $t_1 \And t_2$ stands for two independent tasks carried out at the same time.
For the system it does not matter if the tasks are executed by two people actually in parallel, or by one person who switches between the tasks.
All events sent to the combined task are interleaved into a serial stream of inputs.
The tasks are truly independent of each other, all interleavings are permitted.
Events to $t_1$ and $t_2$ must be prefixed by $\First$(irst) and $\Second$(econd) respectively.
This unambiguously renames the events, removing any source of nondeterminism.

In \CSP, there are two different combinators for parallel composition: parallel and interleave.
The parallel process $P \parallel Q$ can take $P$-steps and $Q$-steps in arbitrary interleaving for actions unique to $P$ and $Q$.
Actions in the alphabets of both $P$ and $Q$ must be taken in synchronisation, so if one process wants to take such a step, it must wait until the other is ready to do so.
Synchronised steps are the only occasion where two processes actually do something at the same time.

The interleaving operator $P \mid\mid\mid Q$ does not synchronise any actions of $P$ and $Q$.
All interleavings are permitted.
Actions that occur in both alphabets are nondeterministically taken by either $P$ or $Q$.

@@

@@

@@

There are several concepts that exist in both languages, like concurrency, or sending values between concurrent agents.
In \TOP however they are meant to be used on a higher level of abstraction, which allows concise declarative description of patterns of collaboration, without worrying about the implementation details of communication.
By focussing on collaboration, \TOP and \TOPHAT lead to high-level specifications closer to real-world workflows which, at the same time, can be used to generate distributive, multi-user applications to support such workflows.

>>>>

Concurrency is the source of parallelism: two things are done at the same time.
%
Using tasks $t_1$ and $t_2$, the parallel combination $t_1 \And t_2$ stands for two independent tasks carried out at the same time.
For the system it does not matter if the tasks are executed by two people actually in parallel, or by one person who switches between the tasks.
All inputs sent to the combined task are interleaved into a serial stream of inputs.
The tasks are truly independent of each other, all interleavings are permitted.
Inputs to $t_1$ and $t_2$ must be prefixed by $\First$(irst) and $\Second$(econd) respectively.
This unambiguously renames the inputs, removing any source of nondeterminism.

In \CSP, there are two different combinators for parallel composition: parallel and interleave.
The parallel process $P \parallel Q$ can take $P$-steps and $Q$-steps in arbitrary interleaving for actions unique to $P$ and $Q$.
Actions in the alphabets of both $P$ and $Q$ must be taken in synchronisation, so if one process wants to take such a step, it must wait until the other is ready to do so.
Synchronised steps are the only occasion where two processes actually do something at the same time.
%
The interleaving operator $P \mid\mid\mid Q$ does not synchronise any actions of $P$ and $Q$.
All interleavings are permitted.
Actions that occur in both alphabets are nondeterministically taken by either $P$ or $Q$.

\fixme{Add something about reactive programming.}

@@

\fixme{Add something about reactive programming.}

@@

\fixme{Add something about reactive programming.}
\fixme{Add combination function for signals that are emitted at the same instant.}

\subsection{Program generation}

\fixme{Add section about generating executable applications?}

@@

There are several concepts that exist for both tasks and processes, like concurrency, or sending values between concurrent agents.
Using tasks, however, they are meant to be used on a higher level of abstraction, which allows concise declarative description of patterns of collaboration, without worrying about the implementation details of communication.
By focussing on collaboration, tasks and \TOPHAT lead to high-level specifications closer to real-world workflows which, at the same time, can be used to generate distributive, multi-user applications to support such workflows.
